\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-17 paper/paper.Rnw
small typos

Where $\psi$ is the logit link function, $\psi(x) = \frac{e^{x}}{1+e^{x}}$, $x_{1}$ is the absolute value of the true plot correlation, with $i \in {0.3, 0.5, 0.7, 0.9}$ $x_{2,j} is a dummy variable for the sign of the true plot correlation, with $j = 0$ for negative correlation, $x_{3,k}$ is a dummy variable for the smoothing procedure, with $k = 0$ for unsmoothed data, $x_{4,t}$ is the sample size, with $t \in {12, 24, 48, 96}$ and $z_{s}$ is an observer specific random effect, with $s = 1, 2, \cdot , 157$

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot model: 900, overlaid lines model: 949, total: 1849. Default plot design is an overlaid lines type. The model is fitted using the glimmix procedure in SAS. Subjects with less than ten lineup evaluations were removed from the sample. %Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample..}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

\begin{table}
\label{tab2}
\centering
\caption{Mixed Linear Model fit for time taken to make a selection}
<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "r", "sign(r)", "r*sign(r)", "correct", "Plot", "Plot*Smoothed", "Plot*t", "Plot*r", "Plot*sign(r)", "Plot*r*sign(r)", "Plot*correct")
kable(time.fit[1:7,], format="latex", caption="Main Effects (Overlaid Lines)")
kable(time.fit[8:14,], format="latex", caption="Interaction Effects (Scatter plot)")
@
\end{table}

>>>>

Where $\psi$ is the logit link function, $\psi(x) = \frac{e^{x}}{1+e^{x}}$, $x_{1}$ is the absolute value of the true plot correlation, with $i \in {0.3, 0.5, 0.7, 0.9}$ $x_{2,j}$ is a dummy variable for the sign of the true plot correlation, with $j = 0$ for negative correlation, $x_{3,k}$ is a dummy variable for the smoothing procedure, with $k = 0$ for unsmoothed data, $x_{4,t}$ is the sample size, with $t \in {12, 24, 48, 96}$ and $z_{s}$ is an observer specific random effect, with $s = 1, 2, \cdot , 157$

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot model: 900, overlaid lines model: 949, total: 1849. Default plot design is an overlaid lines type. The model is fitted using the glimmix procedure in SAS. Subjects with less than ten lineup evaluations were removed from the sample.} %Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample..}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

\begin{table}
\label{tab2}
\centering
\caption{Linear mixed model fit for time taken to make a selection}
<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
time.fit <- summary(timelmer)$coefficients
pv <- function(x){
  p <- 2*(1-pt(x, 1835))
}
p.value <- sapply(time.fit[,3], pv)
time.fit <- cbind(time.fit, p.value)
time.fit <- time.fit[c(1, 2, 4, 3, 5, 8, 7, 6, 9, 11, 10, 12, 14, 13),] #separate into main effects then interaction effects in same order
rownames(time.fit) <- c("Intercept", "Smoothed", "t", "r", "sign(r)", "r*sign(r)", "correct", "Plot", "Plot*Smoothed", "Plot*t", "Plot*r", "Plot*sign(r)", "Plot*r*sign(r)", "Plot*correct")
kable(time.fit[1:7,], format="latex", caption="Main Effects (Overlaid Lines)")
kable(time.fit[8:14,], format="latex", caption="Interaction Effects (Scatter plot)")
@
\end{table}
